### 2015-03-30 README.Rmd
readme image

[Martin Van der Linden](https://martinvdlinden.wordpress.com/) (Dept. of Economics, Vanderbilt University) and [John Nay](https://johnnay.github.io) (School of Engineering, Vanderbilt University).

@@

>>>>

[Martin Van der Linden](https://martinvdlinden.wordpress.com/) (Dept. of Economics, Vanderbilt University) and [John J. Nay](https://johnnay.github.io) (School of Engineering, Vanderbilt University).

@@

Here is a snapshot of the model's network of agents at an intialization:

![alt text](figures/network.png)
